PyPy's Approach to Virtual Machine Construction

### 2006-07-13 talk/dls2006/paper.tex
a paragraph about the jit goal in the intro.

We shortly describe the architecture of PyPy in section
\ref{architecture}.  In section \ref{systemprog} we describe our
approach of varying the type systems at various levels of the
translation.  Section \ref{typeinference} gives an overview of the
type inference engine we developed (and can be read independently from
section 3).  We present experimental results in section
\ref{experimentalresults} and future work directions in section
\ref{futurework}.  In section \ref{relatedwork} we compare with
related work, and finally we conclude in section \ref{conclusion}.

>>>>

Recent projects developing meta-circular interpreters
\cite{KleinVM}\cite{Jikes-JIT}\cite{jalapeno} incorporate a native
compiler directly in their virtual machine design and high-level
implementations. We believe that this is a less evolvable and
maintainable encoding of the semantics of a language than a bytecode
intepreter, especially with languages such as Python for which
internal design simplicity was not a goal from the start or in its
current evolution. Our on-going efforts (beyond the scope of this
paper) aim instead at generating native compilers as a (non-trivial)
step of our translation process (see sections \ref{relatedwork} and
\ref{futurework}). This belief and goal inform our architecture.

In the paper we shortly describe the architecture of PyPy in section
\ref{architecture}.  In section \ref{systemprog} we describe our
approach of varying the type systems at various levels of the
translation.  Section \ref{typeinference} gives an overview of the
type inference engine we developed (and can be read independently from
section 3).  We present experimental results in section
\ref{experimentalresults} and future work directions in section
\ref{futurework}.  In section \ref{relatedwork} we compare with
related work, and finally we conclude in section \ref{conclusion}.
